Uso del tiempo de los ecuatorianos 1

### 2022-04-11 Draft_Articulo1_LIDE_UT.Rmd
Adición de xlim() en uno de los gráficos comparativos

ggplot( df_t_cocina_UT2012_plot4 , aes(x = media_ponderada_horas_cocina , y = reorder(provincia_UT2012, media_ponderada_horas_cocina) )) + 
  geom_bar(stat = 'identity', position = 'dodge', fill = "lightblue") + 
  labs(title = "2012", caption = "") +
  geom_text(aes(label = round(media_ponderada_horas_cocina, digits = 2)  ), color ="#1A374D", size = 4,position = position_dodge(0.9), hjust = 1.2) +
  xlab("Promedio de horas") +
  ylab("Provincia") +
  theme_classic()
,

ggplot( df_t_cocina_UT2019_plot4 %>% 
       mutate(provincia_UT2019 = fct_relevel(provincia_UT2019, 
                                                'Azuay',
                                                'Bolívar',
                                                'Cañar',
                                                'Carchi',
                                                'Chimborazo',
                                                'Cotopaxi',
                                                'El Oro',
                                                'Esmeraldas',
                                                'Guayas',
                                                'Imbabura',
                                                'Loja',
                                                'Los Ríos',
                                                'Manabí',
                                                'Morona Santiago',
                                                'Napo',
                                                'Orellana',
                                                'Pastaza',
                                                'Pichincha',
                                                'Santa Elena',
                                                'Santo Domingo de los Tsáchilas',
                                                'Sucumbíos',
                                                'Tungurahua',
                                                'Zamora Chinchipe',
                                                'Zonas no delimitadas',
                                                'Galápagos')) %>% 
       filter(provincia_UT2019 != 'Galápagos' & provincia_UT2019 != 'Zonas no delimitadas') , aes(x = media_ponderada_horas_cocina , y = reorder(provincia_UT2019, media_ponderada_horas_cocina) )) + 
  geom_bar(stat = 'identity', position = 'dodge', fill = "lightblue") + 
  labs(title = "2019", caption = "") +
  geom_text(aes(label = round(media_ponderada_horas_cocina, digits = 2)  ), color ="#1A374D", size = 4,position = position_dodge(0.9), hjust = 1.2) +
  xlab("Promedio de horas") +
  ylab("Provincia") +
  theme_classic()

>>>>

ggplot( df_t_cocina_UT2012_plot4 , aes(x = media_ponderada_horas_cocina , y = reorder(provincia_UT2012, media_ponderada_horas_cocina) )) + 
  geom_bar(stat = 'identity', position = 'dodge', fill = "lightblue") + 
  xlim(0,6) +
  labs(title = "2012", caption = "") +
  geom_text(aes(label = round(media_ponderada_horas_cocina, digits = 2)  ), color ="#1A374D", size = 4,position = position_dodge(0.9), hjust = 1.2) +
  xlab("Promedio de horas") +
  ylab("Provincia") +
  theme_classic()
,

ggplot( df_t_cocina_UT2019_plot4 %>% 
       mutate(provincia_UT2019 = fct_relevel(provincia_UT2019, 
                                                'Azuay',
                                                'Bolívar',
                                                'Cañar',
                                                'Carchi',
                                                'Chimborazo',
                                                'Cotopaxi',
                                                'El Oro',
                                                'Esmeraldas',
                                                'Guayas',
                                                'Imbabura',
                                                'Loja',
                                                'Los Ríos',
                                                'Manabí',
                                                'Morona Santiago',
                                                'Napo',
                                                'Orellana',
                                                'Pastaza',
                                                'Pichincha',
                                                'Santa Elena',
                                                'Santo Domingo de los Tsáchilas',
                                                'Sucumbíos',
                                                'Tungurahua',
                                                'Zamora Chinchipe',
                                                'Zonas no delimitadas',
                                                'Galápagos')) %>% 
       filter(provincia_UT2019 != 'Galápagos' & provincia_UT2019 != 'Zonas no delimitadas') , aes(x = media_ponderada_horas_cocina , y = reorder(provincia_UT2019, media_ponderada_horas_cocina) )) + 
  geom_bar(stat = 'identity', position = 'dodge', fill = "lightblue") + 
  xlim(0,6) +
  labs(title = "2019", caption = "") +
  geom_text(aes(label = round(media_ponderada_horas_cocina, digits = 2)  ), color ="#1A374D", size = 4,position = position_dodge(0.9), hjust = 1.2) +
  xlab("Promedio de horas") +
  ylab("Provincia") +
  theme_classic()
